### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Updated Final Docs Abstract

\item Ability to pick up objects\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/PickUp.cs}{PickUp.cs}}
\end{itemize}
\newpage
\noindent \textbf{Camera Movement}\\
The camera movement script handles inputs from the mouse and converts them into how the main character perspective camera should be rotated. Additionally, it also rotates the player model and a hidden orientation object which is used to keep track of the direction the user is looking for other functions. The range of motion is restricted with the \texttt{Mathf.Clamp()} function from Unity's Library in such a manner that the user can freely move horizontally but not vertically. 
\\\\
\textbf{Player Movement}\\
The player movement script is responsible for handling all movement based interactions and as such was tested intensively with the values for variables being tweaked constantly. Figure \ref{flrtst} shows the in engine scene where the testing took place at first.

@@

\noindent \textbf{Pick Up}\\
This script provides functionality for the user to interact with objects, specifically the ball object used throughout the game, and be able to pick them up, hold them for a time and throw them when required. It is comprised of three main functions - \texttt{PickUpObject()}, \texttt{DropThrowObject()} and \texttt{MoveObject()}. This script uses a raycast sent towards the centre of the screen and if an object with a rigid body, such as the player (excluded from this script) which is an object that is capable of interacting with the physics engine of the game, is in the path it is picked up by using the E key. Once this is done the object is moved toward the player's hand, shrunken down slightly and the collider of the object made inert. From this point, the object is then moved alongside the player with the linking script and when E is pressed while the player has an object it is launched in the direction the player is looking - that is the centre of the screen.
\\\\
Aside from scripts, a player prefab and crosshair were created. A prefab is a collection of objects, scripts and/or relations set in the editor that can be stored as if it were one object so that it can be "dragged and dropped" as needed. Figure \ref{cross} shows the place holder crosshair that was used until this point and the finalised crosshair. This was implemented to display where the centre of the screen is to a user.

@@

\subsection{Sprint 3: Full Scale Development}

@@

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.45]{Figures/pause.png}
\caption{Pause Menu}
\end{figure}

@@

\section{Description of the Development of the Article}
%Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.

\subsection{Sprint 1: Research Proposal}

>>>>

\item Ability to pick up objects\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/PickUp.cs}{PickUp.cs}}

\item Object Rotation\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/ObjectRotateScript.cs}{ObjectRotateScript.cs}}
\end{itemize}
\newpage
\noindent \textbf{Camera Movement}\\
The camera movement script handles inputs from the mouse and converts them into how the main character perspective camera should be rotated. Additionally, it also rotates the player model and a hidden orientation object which is used to keep track of the direction the user is looking for other functions. The range of motion is restricted with the \texttt{Mathf.Clamp()} function from Unity's Library in such a manner that the user can freely move horizontally but not vertically. 
\\\\
\textbf{Player Movement}\\
The player movement script is responsible for handling all movement based interactions and as such was tested intensively with the values for variables being tweaked constantly. Figure \ref{flrtst} shows the in engine scene where the testing took place at first.

@@

\noindent \textbf{Pick Up}\\
This script provides functionality for the user to interact with objects, specifically the ball object used throughout the game, and be able to pick them up, hold them for a time and throw them when required. It is comprised of three main functions - \texttt{PickUpObject()}, \texttt{DropThrowObject()} and \texttt{MoveObject()}. This script uses a raycast sent towards the centre of the screen and if an object with a rigid body, such as the player (excluded from this script) which is an object that is capable of interacting with the physics engine of the game, is in the path it is picked up by using the E key. Once this is done the object is moved toward the player's hand, shrunken down slightly and the collider of the object made inert. From this point, the object is then moved alongside the player with the linking script and when E is pressed while the player has an object it is launched in the direction the player is looking - that is the centre of the screen.
\\\\
\textbf{Object Rotation}\\
This script, when placed onto any game object like as with the linking script, will cause the object to rotate at a specific speed set in the editor. Figure \ref{rot} demonstrated how this looks. It makes use of the \texttt{RotateAround()} function where the object was rotated around its' downward facing vector.

\begin{figure}[H]
\centering
\includegraphics[scale=1]{Figures/rot.png}
\caption{Object Rotation Set in Editor}
\label{rot}
\end{figure}

\noindent Aside from scripts, a player prefab and crosshair were created. A prefab is a collection of objects, scripts and/or relations set in the editor that can be stored as if it were one object so that it can be "dragged and dropped" as needed. Figure \ref{cross} shows the place holder crosshair that was used until this point and the finalised crosshair. This was implemented to display where the centre of the screen is to a user.

@@

\subsection{Sprint 3: Full Scale Development}
This sprint made use of the base developed in the previous one. During this sprint, the main focus was on developing the game in full based of the work already done. It also included the creation of certain assets, additional scripts, "quality of life" features and the final individual levels. These included:
\begin{itemize}
\item Ball return functionality\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/BallReturn.cs}{BallReturn.cs}}

\item Teleportation functionality \footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/TeleportScript.cs}{TeleportScript.cs}} with the inclusion of a portal prefab

\item Implementation of moving platforms\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/MovingPlatforms.cs}{MovingPlatforms.cs}}

\item Level Switching after completion\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/EndLevel.cs}{EndLevel.cs}}

\item The development of the first level - that being the tutorial.

\item Ability to pause the game and navigate scenes\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/PauseMenu.cs}{PauseMenu.cs}}
\end{itemize}

\textbf{Ball Return}\\

\textbf{Teleportation and Portal Prefab}\\

@@

\textbf{Ending a Level}\\

\textbf{Tutorial Level Development}\\

@@

\textbf{Pause Menu}\\

\begin{figure}[H]
\centering
\includegraphics[scale=0.45]{Figures/pause.png}
\caption{Pause Menu}
\label{pause}
\end{figure}

@@

\section{Description of the Development of the Article}
%Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.
This section will detail the development of the article and the specific sprints taken to complete it.

\subsection{Sprint 1: Research Proposal}
As stated, this is the "Awareness of Problem" process within design science. As the topic the research was to be conducted on was open-ended, this sprint focused on finding a topic. There was a personal interest in educational games and as such it became the first topic to be examined if it was viable for a research study. This included doing research into what issues educational games could solve. The results of this were a list of potential issues ranging from using them to aid psychological treatment to the use of simulations for training. The issue settled on was how they can be used in educational institutions which then lead into further research into acceptance of games and existing academically developed games. 
\\\\
Once this research was completed, a research proposal was drafted and submitted as the conclusion to this step.

### 2021-11-08 Final Doc/main.tex
Final Docs Updated
Added group cont. table
Updated Final Docs
Updated Final Docs Abstract

\documentclass[
12pt, % The default document font size, options: 10pt, 11pt, 12pt
oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
onehalfspacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

\usepackage{graphicx}
\usepackage{float}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[final]{pdfpages}
\usepackage{mathpazo} % Use the Palatino font by default
\usepackage{changepage}
\usepackage{caption}
\usepackage[list=false]{subcaption}
\usepackage[backend=biber,style=apa,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

@@

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
\end{abstract}

@@

\include{Chapters/Chapter1}
\include{Chapters/Chapter2}
\include{Chapters/Chapter3}

@@

\printbibliography[heading=bibintoc]

>>>>

\documentclass[
12pt, % The default document font size, options: 10pt, 11pt, 12pt
oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
onehalfspacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure
\usepackage{minted}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{float}
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international =

\usepackage{booktabs}
\usepackage{multirow}
\usepackage[final]{pdfpages}
\usepackage{mathpazo} % Use the Palatino font by default
\usepackage{changepage}
\usepackage{caption}
\usepackage[list=false]{subcaption}
\usepackage[backend=biber,style=apa,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

@@

\newcommand{\titleAfrikaans}{Die Eienskappe van Speletjies vir Gebruik in Onderwys}

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
Education is a system that had its' last major revision during the industrial age which saw instructional institutions act like factories with the goal of propelling students through the system as quick as possible. Due to this, a curriculum is often standardised and used as a means to teach all students in the same way. The issue with this is that some students may not learn effectively with the modes of education presented. One possible implementation to aid in solving this problem is the inclusion of digital and computer-based serious games into the modes of instruction.
\\\\
This study was focused on identifying possible qualities these types of games should possess to be used effectively within an educational environment. In order to reach this goal, a literature study was conducted on the fields of pedagogy, ludology and gamification with each playing a role in better understanding the means of developing these qualities. Additionally, several case studies concerning serious game artefacts were examined in which the design philosophies of the serious games were discussed and examined to identify any correlation between instructional theories. The results of this section of the project are several key qualities required as well as a brief discussion on how different topics could be approached.
\\\\
Furthermore, this project included the development of an artefact in the form of a digital computer game. These aspects of the project were conducted simultaneously with minimal correlation. The artefact was developed using the Unity Editor and C\# as the main developmental tools. The result of this is a short computer game that has a focus on simple puzzle-solving, platforming and action-based gameplay.
\\\\
\textbf{Keywords:} Game Design and Development, Gamification, Ludology, Pedagogy, Serious Games, Unity

\end{abstract}

\begin{extraAbstract}
\addchaptertocentry{\abstractnameExtra} % Add the abstract to the table of contents
Onderwys is 'n stelsel wat sy laaste groot hersiening tydens die industriële era gehad het, waarin onderriginstellings soos fabrieke opgetree het met die doel om studente so vinnig as moontlik deur die stelsel te dryf. As gevolg hiervan word 'n kurrikulum dikwels gestandaardiseer en gebruik as 'n manier om alle studente op dieselfde manier te onderrig. Die probleem hiermee is dat sommige studente dalk nie effektief leer met die onderrigmetodes wat aangebied word nie. Een moontlike implementering om te help om hierdie probleem op te los, is die insluiting van digitale en rekenaargebaseerde ernstige speletjies in die onderrigmodusse.
\\\\
Hierdie studie was gefokus op die identifisering van moontlike eienskappe wat hierdie tipe speletjies behoort te besit om effektief binne 'n opvoedkundige omgewing gebruik te word. Ten einde hierdie doel te bereik, is 'n literatuurstudie oor die velde van pedagogie, ludologie en gamification gedoen, met elkeen wat 'n rol gespeel het om die maniere om hierdie eienskappe te ontwikkel beter te verstaan. Verder is verskeie gevallestudies oor ernstige speletjie-artefakte ondersoek waarin die ontwerpfilosofieë van die ernstige speletjies bespreek en ondersoek is om enige korrelasie tussen onderrigteorieë te identifiseer. Die resultate van hierdie afdeling van die projek is verskeie sleuteleienskappe wat vereis word, asook 'n kort bespreking oor hoe verskillende onderwerpe benader kan word.
\\\\
Verder het hierdie projek die ontwikkeling van 'n artefak in die vorm van 'n digitale rekenaarspeletjie ingesluit. Hierdie aspekte van die projek is gelyktydig uitgevoer met minimale korrelasie. Die artefak is ontwikkel met behulp van die Unity Editor en C\# as die belangrikste ontwikkelingsinstrumente. Die resultaat hiervan is 'n kort rekenaarspeletjie wat 'n fokus het op eenvoudige legkaartoplossing, platforms en aksie-gebaseerde spel.
\\\\
\textbf{Keywords:} Speletjieontwerp en -ontwikkeling, Gamification, Ludologie, Pedagogie, Ernstige Spele, Unity

\end{extraAbstract}

@@

\include{Chapters/Chapter1}
\include{Chapters/Chapter2}
\include{Chapters/Chapter3}
\include{Chapters/Chapter4} 
\include{Chapters/Chapter5}

@@

\printbibliography[heading=bibintoc,title=Reference List]
